---
title: "Introduction to seeker"
author: "Jake Hughey"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to seeker}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = '#>')
```

The `seeker` package is designed to be an R-based wrapper around various command-line tools. The main function in the `seeker` package is, well, `seeker()`. Currently `seeker()` is targeted at processing bulk RNA-seq data. The main input is a list of parameters specifying which steps of RNA-seq data processing to perform and how to perform them. Depending on the parameters, `seeker()` will call other functions in the package.

A convenient way to construct the list of parameters is to make a yaml file and read it into R using `yaml::read_yaml()`. A template yaml file is reproduced below and available at `system.file('extdata', 'params_template.yml', package = 'seeker')`.

```{r, code = readLines(system.file('extdata', 'params_template.yml', package = 'seeker')), eval = FALSE}
```

A convenient way to run `seeker()` is then using a script such as the one reproduced below and available at `system.file('extdata', 'run_seeker.R', package = 'seeker')`.

```{r, code = readLines(system.file('extdata', 'run_seeker.R', package = 'seeker')), eval = FALSE}
```

If you copy the script to your current working directory, you can run it using something like

```sh
Rscript run_seeker.R <path/to/study>.yml <path/to/parent/directory>
```

A fancier option, which saves stdout and stderr to a log file, would be something like

```sh
study="<study>" && \
parentDir="<path/to/parent/directory>" && \
mkdir -p "${parentDir}/${study}" && \
Rscript run_seeker.R "<path/to>/${study}.yml" "${parentDir}" &> \
  "${parentDir}/${study}/progress.log"
```

This option assumes that the name of the yaml file (minus the file extension) is identical to the `study` variable within the yaml file, which we highly recommend.
